---
title: "AML "
output: html_notebook
---

This dataset comes from the Basel Institute on Governance, which issues an [annual ranking of countries' AML risk](https://www.baselgovernance.org/basel-aml-index/public-ranking)

0=Low Risk 10=High Risk

```{r}
library(readxl)
library(dplyr)
library(stringr)

amlDf <- read_excel('public_basel_aml_index_rankings_2012-2018_0_0.xls')
amlDf
```

We have 151 rows - a few less than the financial inclusion data. Interesting. The good news is that the year is 2017, which matches the financial inclusion data. I had been worried that it would be data for 2018.

```{r}
newCols <- c("Country", "Score", "Ranking")
colnames(amlDf) <- newCols
amlDf


```

```{r}
# get rid of the first row (0=Low Risk 10 = High Risk)
amlDf <- amlDf %>% filter(is.na(Score)==F)
amlDf


```

## Notice that several of the countries end with an asterisk. The corresponding footnote isn't relevant to my project, so I want to remove the asterisks. First, let's see how many there are.
```{r}
starred <- amlDf %>% filter(endsWith(Country, "*"))
starred
```
There are 26 - too many to change individually. So, let's think about how to remove them all with one piece of code.


```{r}
# use the stringr method str_remove().

# create a separate vector
starredCountries <- starred$Country

# call the str_remove method on the vector. the second argument is the character you want to replace.
starredCountries <- str_remove(starredCountries, '[*]')

# put the amended vector into the dataframe
starred <- starred %>% mutate(Country=starredCountries)

starred
 

```

## Let's try the `str_remove()` method on the main dataframe.
```{r}
countries <- amlDf$Country
countries <- str_remove(countries, '[*]')

amlDf <- amlDf %>% mutate(Country=countries)
amlDf
```
Success!

## Let's create a csv file.
```{r}
write.csv(amlDf, 'aml_rankings_2017.csv')
```


 