---
title: "R Notebook"
output: html_notebook
---
 

```{r}
library(readr)
library(dplyr)

findex <- read.csv('findex_2017_cleaned.csv')

findex <- findex %>% select(`Country.Name`, `Financial.Inclusion`)
head(findex)
nrow(findex)
 
```

```{r}
amlRisk <- read.csv('amlRisk_2017_cleaned.csv')
amlRisk <- amlRisk %>% select(Country, `AML.Risk`)
head(amlRisk)
nrow(amlRisk)
```

```{r}

row1 <- c(1,NA)
row2 <- c(3,NA)

findex2 <- rbind(findex, row1)
findex2 <- rbind(findex2, row2)
#findex2 <- findex2 %>% mutate(`Country.Name`=as.character(`Country.Name`))
#findex2 <- findex2 %>% mutate(`Country.Name`=replace(`Country.Name`, `Financial.Inclusion`=="Extra", "Extra"))
#findex2 <- findex2 %>% mutate(`Country.Name`=replace(`Country.Name`, `Financial.Inclusion`=="Bonus", "Bonus"))

findex2
# combined <- amlRisk %>% cbind(findex)
# combined
```

```{r}
combined <- amlRisk %>% cbind(findex2)
combined
```

# missing from FINDEX
Angola
Cape Verde
Gambia
Grenada
Guinea-Bissau
Guyana
Iceland
Lithuania
Marhsall Islands
Papua New Guinea
Qatar
Sao Tome and Principe
Sudan
St. Lucia
St. Vincent And The Grenadines
Timor-Leste (East Timor)
Vanuatu
Yemen

# missing from AML
Belarus
Cameroon
Congo, Dem Rep? 
Congo, Rep? 
Dominica
Guinea
Iraq
Kosovo
Madagascar
South Sudan
Turkmenistan
West Bank and Gaza

## filter out unwanted rows from findex
```{r}

findex <- findex %>% filter(`Country.Name`!='Belarus')
findex <- findex %>% filter(`Country.Name`!='Cameroon')
findex <- findex %>% filter(`Country.Name`!='Congo, Dem. Rep.')
findex <- findex %>% filter(`Country.Name`!='Congo, Rep.')
findex <- findex %>% filter(`Country.Name`!='Dominica')
findex <- findex %>% filter(`Country.Name`!='Guinea')
findex <- findex %>% filter(`Country.Name`!='Iraq')
findex <- findex %>% filter(`Country.Name`!='Kosovo')
findex <- findex %>% filter(`Country.Name`!='Madagascar')
findex <- findex %>% filter(`Country.Name`!='South Sudan')
findex <- findex %>% filter(`Country.Name`!='Turkmenistan')
findex <- findex %>% filter(`Country.Name`!='West Bank and Gaza')
findex <- findex %>% filter(`Country.Name`!='Central African Republic')
findex <- findex %>% filter(`Country.Name`!='Chad')
findex <- findex %>% filter(`Country.Name`!='Gabon')
findex <- findex %>% filter(`Country.Name`!='Ethiopia')
findex <- findex %>% filter(`Country.Name`!='Libya')
findex <- findex %>% filter(`Country.Name`!='Lithuania')
findex <- findex %>% filter(`Country.Name`!='Togo')
findex

```

## filter out unwanted rows from amlRisk
```{r}
amlRisk <- amlRisk %>% filter(Country!='Angola')

amlRisk <- amlRisk %>% filter(Country!='Cape Verde')
amlRisk <- amlRisk %>% filter(Country!='Gambia')

amlRisk <- amlRisk %>% filter(Country!='Grenada')
amlRisk <- amlRisk %>% filter(Country!='Guinea-Bissau')
amlRisk <- amlRisk %>% filter(Country!='Guyana')
amlRisk <- amlRisk %>% filter(Country!='Iceland')
amlRisk <- amlRisk %>% filter(Country!='Lithuania')
amlRisk <- amlRisk %>% filter(Country!='Marshall Islands')
amlRisk <- amlRisk %>% filter(Country!='Papua New Guinea')
amlRisk <- amlRisk %>% filter(Country!='Qatar')
amlRisk <- amlRisk %>% filter(Country!='Sao Tome And Principe')
amlRisk <- amlRisk %>% filter(Country!='Sudan')
amlRisk <- amlRisk %>% filter(Country!='St. Lucia')
amlRisk <- amlRisk %>% filter(Country!='St. Vincent And The Grenadines')
amlRisk <- amlRisk %>% filter(Country!='Timor-Leste (East Timor)')
amlRisk <- amlRisk %>% filter(Country!='Vanuatu')
amlRisk <- amlRisk %>% filter(Country!='Yemen')
amlRisk <- amlRisk %>% filter(Country!='Dominica')
amlRisk <- amlRisk %>% filter(Country!='Jamaica')

amlRisk
# Angola
# Cape Verde
# Gambia
# Grenada
# Guinea-Bissau
# Guyana
# Iceland
# Lithuania
# Marhsall Islands
# Papua New Guinea
# Qatar
# Sao Tome and Principe
# Sudan
# St. Lucia
# St. Vincent And The Grenadines
# Timor-Leste (East Timor)
# Vanuatu
# Yemen


```

## they seem to be equal, so let's try and add them together
```{r}
combined <- amlRisk %>% cbind(findex)
combined


```


```{r}
# reorder the columns so that country names are next to each other (so I can check them)
newOrder <- c('Country', 'Country.Name', 'AML.Risk', 'Financial.Inclusion')
combined2 <- combined[, newOrder]
combined2
```
## let's clean this a bit more.
```{r}
# get rid of Country.Name
combined2 <- combined2 %>% select(-Country.Name)

library(stringr)
combined2 <- combined2 %>% mutate(Country=as.character(Country))

combined2 <- combined2 %>% mutate(Country=replace(Country, str_detect(Country, "Taiwan"), "Taiwan"))

combined2
```

