---
title: "Combining the Inclusion and AML Risk datasets"
output: html_notebook
---

In `Findex.Rmd` I imported and cleaned Financial Inclusion data, and created a dataset `findex_2017.csv`.
In `AmlRanking.Rmd` I imported and cleaned AML Risk data, and created a dataset `aml_rankings_2017.csv`.
In the present notebook I will combine these two datasets.

## Problems
1. The two datasets do not deal with the same countries: there are 159 countries in `findex_2017.csv` and 147 countries in `aml_rankings_2017.csv`.
2. The data may not be in the same order. We might assume they are in alphabetical order, but that may not be the case.

## How I intend to solve the problems
1. Let's get more information on the problem, by comparing the two datasets.
2. We can reorder one or both the datasets if necessary.

## Problem 1: finding out which countries are missing from the lists
```{r}
library(readr)
library(dplyr)

findex <- read.csv('findex_2017.csv')

# The first 22 rows are country groupings (such as 'World' and 'High income'), so let's filter them out
findex <- findex %>% filter(X>22)

# While we're cleaning, let's also rename the 'X2017' column to 'Financial Inclusion'

findex <- findex %>% rename(`Financial Inclusion`=X2017)

findex <- findex %>% mutate(`Country.Name`=as.character(`Country.Name`))

findex



```

# get  list of the countries 
```{r}

inclusionCountries <- findex$Country.Name
inclusionCountriesData <- data.frame(inclusionCountries)
inclusionCountriesData <- inclusionCountriesData %>% rename(Country=inclusionCountries)
inclusionCountriesData
```

## import and clean AmlRankings
```{r}

amlRisk <- read.csv('aml_rankings_2017.csv')
amlRisk

# The first row shouldn't be there (it's actually a header), so delete it
# The first 22 rows are country groupings (such as 'World' and 'High income'), so let's filter them out
amlRisk <- amlRisk %>% filter(X!=1)

# While we're cleaning, let's also rename the 'Score' column to 'AML Risk' 

amlRisk <- amlRisk %>% rename(`AML Risk`=Score)

# and let's also delete Ranking
amlRisk <- amlRisk %>% select(-Ranking)

amlRisk <- amlRisk %>% mutate(Country=as.character(Country))

amlRisk

```

# get  list of the AmlRisk countries 
```{r}
amlCountries <- amlRisk$Country
amlCountriesData <- data.frame(amlCountries)
#inclusionCountriesData


amlCountriesData <- amlCountriesData %>% rename(Country=amlCountries)
amlCountriesData
```


```{r}

combinedData <- amlCountriesData %>% full_join(inclusionCountriesData)
combinedData <- combinedData %>% arrange(Country)
combinedData

# excludedAmlCountries <- amlCountries[!(amlCountries %in% inclusionCountries)]
# class(excludedAmlCountries)


#excludedInclusionCountries <- inclusionCountries[!(inclusionCountries %in% amlCountries)]
#excludedInclusionCountries

#bothExcluded <- c(excludedInclusionCountries, excludedAmlCountries)
 
#bothExcluded
```

## tidy up where the same country has different names
```{r}
# Same country, different name
# Bosnia and Herzegovina - Bosnia-Herzegovina - change AML
# Congo, Dem. Rep - Congo, Rep - no, they are different - 
# Cote d'Ivoire - Cote D'ivoire - change AML
# Egypt - Egypt, Arab Rep. - change Findex DONE
# Guinea - Guinea-Bissau - no, they are different
# Hong Kong Sar, China - Hong Kong SAR, China - change AML
# Iran - Iran, Islamic Rep. - change FINDex  DONE
# Korea, Rep. - Korea, South - change findex- DONE
# Kyrgyz Republic - Kyrgyzstan - change findex DONE 
# Lao PDR - Laos - change findex DONE
# Macedonia - Macedonia, FYR - change findex DONE
# Slovak Republic - Slovakia - change findex DONE 
# Russia - Russian Federation - change findex DONE
# Venezuela - Venezuela, RB - change findex DONE

```

```{r}

# replace the names in findex. For some reason, it's not letting me do this with vectors, so I will do it the slow way.

findex <- findex %>% mutate(`Country.Name`=replace(`Country.Name`, `Country.Name`=='Egypt, Arab Rep.', 'Egypt'))

findex <- findex %>% mutate(`Country.Name`=replace(`Country.Name`, `Country.Name`=='Iran, Islamic Rep.', 'Iran'))

findex <- findex %>% mutate(`Country.Name`=replace(`Country.Name`, `Country.Name`=='Korea, Rep.', 'Korea, South'))

findex <- findex %>% mutate(`Country.Name`=replace(`Country.Name`, `Country.Name`=='Kyrgyz Republic', 'Kyrgyzstan'))

findex <- findex %>% mutate(`Country.Name`=replace(`Country.Name`, `Country.Name`=='Lao PDR', 'Laos'))

findex <- findex %>% mutate(`Country.Name`=replace(`Country.Name`, `Country.Name`=='Macedonia, FYR', 'Macedonia'))

findex <- findex %>% mutate(`Country.Name`=replace(`Country.Name`, `Country.Name`=='Russian Federation', 'Russia'))

findex <- findex %>% mutate(`Country.Name`=replace(`Country.Name`, `Country.Name`=='Slovak Republic', 'Slovakia'))

findex <- findex %>% mutate(`Country.Name`=replace(`Country.Name`, `Country.Name`=='Venezuela, RB', 'Venezuela'))

# findex <- findex %>% mutate(`Country.Name`=replace(`Country.Name`, `X`==c(60,79,88,91,92,100,131,138,162), c('Egypt', 'Iran', 'South Korea', 'Kyrgyzstan', 'Laos', 'Macedonia', 'Russia', 'Slovakia', 'Venezuela')))



# `Country.Name`==c('Egypt, Arab Rep.', 'Iran, Islamic Rep.', 'Korea, Rep.', 'Kyrgyz Republic', 'Lao PDR', 'Macedonia, FYR', 'Russian Federation', 'Slovak Republic', 'Venezuela, RB'), 

findex


```

```{r}
# replace the names in amlRisk

amlRisk <- amlRisk %>% mutate(Country=replace(Country, Country=='Hong Kong Sar, China', 'Hong Kong SAR, China'))

 
amlRisk <- amlRisk %>% mutate(Country=replace(Country, Country=='Bosnia-Herzegovina', 'Bosnia and Herzegovina')) 
 
 
# Cote d'Ivoire - Cote D'ivoire - change AML
amlRisk <- amlRisk %>% mutate(Country=replace(Country, Country=="Cote D'ivoire", "Cote d'Ivoire"))

amlRisk <- amlRisk %>% arrange(Country)
amlRisk
```

```{r}
library(readr)
write.csv(findex, 'findex_2017_cleaned.csv')


```

```{r}
write.csv(amlRisk, 'amlRisk_2017_cleaned.csv')
```

